\maketitleofchinese{基于 WebGL 的 AR 校园交互系统}{吴鼎}{\LaTeX }

\abstractofchinese{随着计算机 CPU 与 GPU 处理器的性能提升以及以 Chrome 浏览器为代表的现代浏览器规范化，统一化发展。3D 图形技术以及以图像识别或标记捕捉为基础的 AR 技术已经能不再局限于 Unity3D 等固有框架。在移动设备浏览器上，以 WebGL 为基础的跨平台 3D 技术；以 AR.js 为基础，调用谷歌公司 ARCore 或苹果公司 ARKit 实现的 AR 技术也逐步走向应用市场。本系统结合 WebGL 与 AR.js 技术实现一套以校园环境为背景的交互系统。核心功能上实现了 3D 模型的显示，操作，对现实场景的识别以及与现实环境的交互。具体技术上，系统采用最新的技术框架: React 构建整体框架，Three.js 实现 WebGL 功能，AR.js 实现场景识别功能，Three.js 结合 AR.js 实现场景交互功能。本系统最大的优势为完全基于浏览器，不需要下载任何额外应用或插件，仅调用移动端底层服务，在跨平台，兼容性上补足了传统 AR 技术依赖软件与操作系统的短板。同时本系统完全使用开源技术实现 AR 功能，不存在任何技术壁垒。}{WebGL；AR；Three.js；图像识别；标记捕捉}

\maketitleofenglish{AR campus interaction system based on WebGL
}{Ding Wu}{School of software}

\abstractofenglish{With the performance improvement of computer CPU and GPU processor and the standardization and development of modern browsers represented by the Chrome browser. 3D graphics and AR technologies based on image recognition or marker recognition are no longer limited to inherent frameworks like Unity3D. WebGL-based cross-platform 3D technology on mobile device browsers; Based on AR.js, AR technology implemented by calling Google's ARCore or Apple's ARKit is also gradually moving towards the application market. This system combines WebGL and AR.js technology to realize an interactive system with the campus environment as the background. The core functions realize the display, operation, recognition of real scenes and interaction with real environments of 3D models. Specifically, the system adopts the latest technical framework: React builds the overall framework, Three.js implements WebGL functions, AR.js implements scene recognition functions, and Three.js combines AR.js to implement scene interaction functions. The biggest advantage of this system is that it is completely browser-based, does not need to download any additional applications or plug-ins, and only calls the underlying services of the mobile terminal, which makes up for the shortcomings of traditional AR technology relying on software and operating system in terms of cross-platform and compatibility. At the same time, this system completely realize AR function using open source technology, there are no technical barriers.}{WebGL；AR；Three.js；image tracking；marker capture}